
\begin{thebibliography}{30}

\bibitem{tabor97} S. L. Tabor, J. D\"oring, G. D. Johns, R. A. Kaye, G. N. Sylvan,
C. J. Gross, Y. A. Akovali, C. Baktash, D. W. Stracener, P. F. Hua, M. Korolija,
D. R. LaFosse, D. G. Sarantites, F. E. Durham, I. Y. Lee, A. O. Macchiavelli,
W. Rathbun, and A. Vander Molen, Phys. Rev. C {\textbf{56}}, 142 (1997).

\bibitem{wiedeking00}  M. Wiedeking, R. A. Kaye, G. Z. Solomon, S. L. Tabor, J. D\"oring,
G. D. Johns, F. Cristancho, M. Devlin, F. Lerma, D. G. Sarantites, I. Y. Lee, and 
A. O. Macchiavelli, Phys. Rev C {\textbf{62}}, 024316 (2000).

\bibitem{doering00} J. D\"oring, Y. A. Akovali, C. Baktash, F. E. Durham, C. J. Gross,
P. F. Hua, G. D. Johns, M. Korolija, D. R. LaFosse, I. Y. Lee, A. O. Macchiavelli,
W. Rathbun, D. G. Sarantites, D. W. Stracener, G. Z. Solomon, S. L. Tabor,
A. Vander Molen, A. V. Afanasjev, and I. Ragnarsson, Phys. Rev. C {\textbf{61}}, 034310
(2000).

\bibitem{jungclaus91} A. Jungclaus, K. P. Lieb, C. J. Gross, J. Heese, D. Rudolph, D. J. Blumenthal, P. Chowdhury, P. J. Ennis, C. J. Lister, Ch. Winter, J. Eberth, S. Skoda, M. A. Bentley, W. Gelletly, and B. J. Varley, Z. Phys. A {\textbf{340}}, 125 (1991).

\bibitem{min91} B. J. Min, S. Suematsu, S. Mitarai, T. Kuroyanagi, K. Heiguchi, and M. Matsuzaki, Nucl. Phys. {\textbf{A530}}, 211 (1991).

\bibitem{kast95} D. Kast, K. P. Lieb, C. J. Gross, A. Jungclaus, D. Rudolph, R. Schubart, H. Grawe, and J. Heese, Nucl. Phys. {\textbf{A587}}, 202 (1995).

\bibitem{lafosse97} D. R. LaFosse, M. Devlin, M. Korolija, F. Lerma, D. G. Sarantites, Y. A. Akovali, C. Baktash, C. J. Gross, D. W. Stracener, J. D\"oring, G. D. Johns, S. L. Tabor, F. E. Durham, I. Y. Lee, A. O. Macchiavelli, and W. Rathbun, Phys. Rev. Lett. {\textbf{78}}, 614 (1997).

\bibitem{weiszflog95} M. Weiszflog, J. Billowes, J. Eberth, C. J. Gross, M. K. Kabadiyski, K. P. Lieb, T. Mylaeus, and D. Rudolph, Nucl. Phys. {\textbf{A584}}, 133 (1995).

\bibitem{teich98} C. Teich, A. Jungclaus, and K. P. Lieb, Nucl. Instrum. Meth. in Phys. Res. {\textbf{A418}}, 365 (1998).

\bibitem{jungclaus98a} A. Jungclaus, V. Fischer, D. Kast, K. P. Lieb, C. Lingk, C. Teich, C. Ender, T. H\"artlein, F. K\"ock, D. Schwalm, J. Billowes, A. Dewald, J. Eberth, R. Peusquens, H. G. Thomas, J. Reif, M. G\'orska, and H Grawe, Nuovo Cimento {\textbf{A111}}, 719 (1998).

\bibitem{jungclaus98b} A. Jungclaus, C. Teich, V. Fischer, D. Kast, K. P. Lieb, C. Lingk, C. Ender, T. H\"artlein, F. K\"ock, D. Schwalm, J. Billowes, J. Eberth, and H. G. Thomas, Phys. Rev. Lett. {\textbf{80}}, 2793 (1998).

\bibitem{teich99} C. Teich, A. Jungclaus, V. Fischer, D. Kast, K. P. Lieb, C. Lingk, C. Ender, T. H\"artlein, F. K\"ock, D. Schwalm, J. Billowes, J. Eberth, and H. G. Thomas, Phys. Rev. C {\textbf{59}}, 1943 (1999).

\bibitem{rudolph96} D. Rudolph, K. P. Lieb, and H. Grawe, Nucl. Phys. {\textbf{A597}}, 298 (1996).

\bibitem{herndl97} H. Herndl and B. A. Brown, Nucl. Phys. {\textbf{A627}}, 35 (1997).

\bibitem{doering99} J. D\"oring, G. D. Johns, R. A. Kaye, M. A. Riley, and S. L. Tabor, Phys. Rev. C {\textbf{60}}, 014314 (1999). 

\bibitem{sarantites96} D. G. Sarantites, P. F. Hua, M. Devlin, L. G. Sobotka, J. Elson, J. T. Hood, D. R. LaFosse, J. E. Sarantites, and M. R. Maier, Nucl. Instr. Meth. in Phys. Res. {\textbf{A381}}, 418 (1996).

\bibitem{lee90} I. Y. Lee, Nucl. Phys. {\textbf{A520}}, 641c (1990).

\bibitem{jin95} H.-Q. Jin, C. Baktash, M. J. Brinkman, C. J. Gross, D. G. Sarantites, I. Y. Lee, B. Cederwall, F. Cristancho, J. D\"oring, F. E. Durham, P.-F. Hua, G. D. Johns, M. Korolija, D. R. LaFosse, E. Landulfo, A. O. Macchiavelli, W. Rathbun, J. X. Saladin, D. W. Stracener, S. L. Tabor, and T. R. Werner, Phys. Rev. Lett. {\textbf{75}}, 1471 (1995).

\bibitem{rudolph962} D. Rudolph, C. J. Gross, Y. A. Akovali, C. Baktash, J. D\"oring, F. E. Durham, P.-F. Hua, G. D. Johns, M. Korolija, D. R. LaFosse, I. Y. Lee, A. O. Macchiavelli, W. Rathbun, D. G. Sarantites, D. W. Stracener, S. L. Tabor, A. V. Afanasjev, and I. Ragnarsson, Phys. Rev. C {\textbf{54}}, 117 (1996).

\bibitem{schnare97} H. Schnare, G. Winter, L. K\"aubler, J. Reif, R. Schwengner, J. D\"oring, G. D. Johns, S. L. Tabor, C. J. Gross, Y. A. Akovali, C. Baktash, D. W. Stracener, F. E. Durham, P. F. Hua, M. Korolija, D. R. LaFosse, D. G. Sarantites, I. Y. Lee, A. O. Macchiavelli, W. Rathbun, and A. Vander Mollen, Phys. Rev. C {\textbf{56}}, 729 (1997).

\bibitem{krane73} K. S. Krane, R. M. Steffen, and R. M. Wheeler, Nucl. Data Tables {\textbf{11}}, 351 (1973).

\bibitem{moore88} E. F. Moore, P. D. Cottle, C. J. Gross, D. M. Headly, U. J. 
H\"uttmeier, S. L. Tabor, and W. Nazarewicz, Phys. Rev. C {\textbf{38}}, 696 (1988).

\bibitem{ziegler00} J. F. Ziegler, J. P. Biersack, and U. Littmark, "The Stopping and Range of Ions in Matter", Pergamon Press, New York, 1985,Ā and www.SRIM.org. (SRIM version 2000.40).

\bibitem{ragnarsson86} I. Ragnarsson, Z. Xing, T. Bengtsson, and M. A. Riley, Phys. Scr. {\textbf{34}}, 651 (1986).

\bibitem{bengtsson85} T. Bengtsson and I. Ragnarsson, Nucl. Phys. {\textbf{A436}}, 14 (1985).

\bibitem{afanasjev99} A. V. Afanasjev, D. B. Fossan, G. J. Lane, and I. Ragnarsson,
Phys. Rep. {\textbf{322}}, 1 (1999).

\bibitem{afanasjev95} A. V. Afanasjev and I. Ragnarsson, Nucl. Phys. {\textbf{A591}}, 387 (1995).

\bibitem{galeriu86} D. Galeriu, D. Bucurescu, and M. Ivascu, J. Phys. G {\textbf{12}}, 329 (1986).

\bibitem{svensson98} C. E. Svensson, C. Baktash, G. C. Ball, J. A. Cameron, M. Devlin, J. Eberth, S. Flibotte, A. Galindo-Uribarri, D. S. Haslip, V. P. Janzen, D. R. LaFosse, I. Y. Lee, A. O. Macchiavelli, R. W. MacLeod, J. M. Nieminen, S. D. Paul, D. C. Radford, L. L. Riedinger, D. Rudolph, D. G. Sarantites, H. G. Thomas, J. C. Waddington, D. Ward, W. Weintraub, J. N. Wilson, A. V. Afanasjev, and I. Ragnarsson, Phys. Rev. Lett. {\textbf{80}}, 2558 (1998).

\bibitem{ragnarsson95} I. Ragnarsson, V. P. Janzen, D. B. Fossan, N. C. Schmeing, and R. Wadsworth, Phys. Rev. Lett. {\textbf{74}}, 3935 (1995).

\bibitem{wadsworth98} R. Wadsworth, R. M. Clark, J. A. Cameron, D. B. Fossan, I. M. Hibbert, V. P. Janzen, R. Kr\"ucken, G. J. Lane, I. Y. Lee, A. O. Macchiavelli, C. M. Parry, J. M. Sears, J. F. Smith, A. V. Afanasjev, and I. Ragnarsson, Phys. Rev. Lett. {\textbf{80}}, 1174 (1998).

\bibitem{chowdhury91} P. Chowdhury, C. J. Lister, D. Vretenar, Ch. Winter, V. P. Janzen, H. R. Andrews, D. J. Blumenthal, B. Crowell, T. Drake, P. J. Ennis, A. Galindo-Uribarri, D. Horn, J. K. Johansson, A. Omar, S. Pilotte, D. Pr\'evost, D. Radford, J. C. Waddington, and D. Ward, Phys. Rev. Lett. {\textbf{67}}, 2950 (1991).

\bibitem{womble93} P. C. Womble, J. D\"oring, T. Glasmacher, J. W. Holcomb, G. D. Johns, T. D. Johnson, T. J. Petters, M. A. Riley, V. A. Wood, and S. L. Tabor, Phys. Rev. C {\textbf{47}}, 2546 (1993).

\end{thebibliography}

